Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-06-02 SDSS Presentation/SDSS Presentation.Rmd
format

---
# Unsupervised Analysis
<br>

@@

# Dashboard Layout Iterations

@@

# Dashboard Components

@@

# Reasoning behind using PCP

@@

# PCPs Effectiveness & Novice Users

@@

NOVIS Model has been used to compare other graphs such as PCP, Tree Maps and Chord diagrams, which helps with the understanding of why we could use the PCPs. We will use this model to ask questions of our town leaders to gain feedback on what they understand.
---

# PCP in Dashboard Develop Reasoning
<br>
+ The large set of publicly available data we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture.

@@

---
class:primary

# Background of Guided Discovery Learning

@@

# Guided Discovery Learning with Dashboard Design
<br>
We leverage the framework of Guided Discovery Learning (GDL) to guide the town leaders to make discoveries using our interactive visualization. By leveraging:

@@

---
# User Testing in Beta

@@

---
# Dashbaord Feedback

>>>>

---
# Dashboard Design Workflow

## Unsupervised Analysis
<br>

@@

---
# Dashboard Design Workflow (Layout)

## Dashboard Layout Iterations

@@

---
# Dashboard Design Workflow (Layout)

## Dashboard Components

@@

---
# Dashboard Philosophy

## Reasoning behind using PCP

@@

# Dashboard Philosophy

## PCPs Effectiveness & Novice Users

@@

NOVIS Model has been used to compare other graphs such as PCP, Tree Maps and Chord diagrams, which helps with the understanding of why we could use the PCPs. We will use this model to ask questions of our town leaders to gain feedback on what they understand.
---
# Dashboard Philosophy

## PCP in Dashboard Develop Reasoning

<br>
+ The large set of publicly available data we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture.

@@

---
class:primary
# Dashboard Philosophy

## Background of Guided Discovery Learning

@@

---
# Dashboard Philosophy

## Guided Discovery Learning with Dashboard Design
<br>
We leverage the framework of Guided Discovery Learning (GDL) to guide the town leaders to make discoveries using our interactive visualization. By leveraging:

@@

---
# Dashboard Design WorkFlow (Feedback)

## User Testing in Beta

@@

---
# Dashboard Design WorkFlow (Feedback)

## Dashbaord Feedback
